Build azimuth compatible fetal kidney reference from the kidney cell atlas

### 2024-08-09 analyses/cell-type-wilms-tumor-06/00_fetal_reference_kidney.Rmd
Update analyses/cell-type-wilms-tumor-06/00_fetal_reference_kidney.Rmd
Co-authored-by: Jaclyn Taroni <19534205+jaclyn-taroni@users.noreply.github.com>

# The current data directory, found within the repository base directory
data_dir <- file.path(repository_base, "data", "2024-07-08", "SCPCP000006")

@@

```{r path_to_output}
path_to_output <- file.path(module_base, "marker-sets")
```

>>>>

# The current data directory, found within the repository base directory
data_dir <- file.path(repository_base, "data", "current", "SCPCP000006")

@@

```{r path_to_output}
path_to_output <- file.path(module_base, "results", "references")
```
